
---
title: "The Effect of Youth Unemployment on Youth Political Engagement"
author: "Tori Dykes & Mansi Wadhwa"
date: "12/2/2016"
output: ioslides_presentation
css: styles.css

---

```{r, warnings=F, message=F, echo=F, include=FALSE}

source("PresentationDataCleaning.R")

```

## Research Question

- How does youth unemployment affect youth political engagement within European countries?
  
- Does it inspire <b>apathy</b> or <b>action</b>?

<b>Hypothesis:</b> Higher youth unemployment will lead to greater levels of interest and engagement in politics. 

## Data Sources

We used two main datasets for our research:

<b>The European Social Survey</b>

- Representative survey of EU residents conducted every two years (we used data from 2002 - 2012)

- Respondents are asked about their opinions and attitudes on a variety of political and social topics

- Subsetted data to only look at youths 18 - 25

<b>Eurostat Data</b>

- Used their data on yearly youth unemployment rates in various European countries 


## Overview: Unemployment Levels 2008 & 2010

```{r, echo = F}
Unemp0810 <- subset(YouthData, YouthData$TIME==2008 | YouthData$TIME==2010)

Unemp0810$TIME <- factor(Unemp0810$TIME) # Ensure year is treated as levels, not as continuous numbers

Unemp0810 <- group_by(Unemp0810, cntry, TIME)


Unemp0810$Value <- as.numeric(as.character(Unemp0810$Value)) # Ensure all the unemployment value are numerics 

ggplot(data=Unemp0810, aes(x=cntry, y=Value, fill=TIME)) + geom_bar(stat="identity", position=position_dodge()) + labs(x="Country", y="Unemployment Rate (% of active population)") + ggtitle("Youth Unemployment Rates in Europe, 2008 - 2010")

```

## Trends in Political Interest Across Countries ## 

```{r, echo = F, warning = F, message = F}
compare <- subset(YouthData, YouthData$cntry == "DE"|YouthData$cntry == "DK"|YouthData$cntry == "ES"|YouthData$cntry == "FR"|YouthData$cntry == "HU"|YouthData$cntry == "IE"|YouthData$cntry == "NL")

ggplot(data = compare, aes(x=TIME, y=avgpolintr)) + geom_line(aes(colour=cntry)) + scale_x_continuous(name="Years", breaks = c(2002, 2004, 2006, 2008, 2010, 2012),labels=c("2002","2004","2006","2008","2010","2012"), limits = c(2002,2012))
```

## Trends in Political Interest Across Education Levels ##

```{r, echo = F}

library(sjPlot)

sjp.setTheme(title.align = "center", title.size = 1.5)
sjp.grpfrq(ESSData$eisced, ESSData$polintr, show.prc = F, show.n = F, 
           axis.titles = c("Education Levels","Frequency"), 
           axis.labels = c("Less than Secondary","Lower \nSecondary","Lower Tier Upper \nSecondary",
                           "Upper Tier Upper \nSecondary","Advanced Vocational","BA","MA"),
           title = c("Distribution of Political Interest by Educational Level"))

```

## Inferential Statistics I: Initial Attempt ## {.smaller .build}

- Original intent was to regress the change in a given political variable on the change in unemployment

- Became clear we simply didn't have the right data / enough data to do this meaningfully

<div class="columns-2">

```{r, echo = F, results='asis'}

m1.1 <- lm(deltaavgpolintr ~ deltavalue, data = YouthData)

m1.1labels <- c("Delta Unemployment")
stargazer::stargazer(m1.1, covariate.labels = m1.1labels, type = "html")

m1.2 <- lm(deltaavgvote ~ deltavalue, data = YouthData)

stargazer::stargazer(m1.2, covariate.labels = m1.1labels, type = "html")


```

</div>

## Inferential Statistics II: Individual-Level Analysis {.smaller}

- Decided to look at individual-level ESS data instead for additional insight

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Survey asks people for their employment status

- Within the paper, would like to look at at least three different measurements for political engagement 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Level of political interest

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Participation in public demonstrations

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Voting

- For this presentation, will focus on <b>political interest</b>

```{r, echo=F}

#Control Variables:
# - eisced
# - pdjobev
# - Countries
# - mbtru
# - gndr
# - stfdem

```

## Inferential Statistics III: Political Interest ##  {.build .morereduced}
```{r, echo=F, results = 'asis'}
## Models for Unemployment ##

# maybe helpful for font sizes: http://www.itgo.me/a/4995744297035700956/resize-stargarzer-table-when-type-html-for-ioslides-in-rstudio

# Political Interest 

m3.1a <- lm(polintr ~ unempdummy, data = ESSData)

m3.1b <- lm(polintr ~ unempdummy + gndr + factor(eisced) - 1 + uniondummy, data = ESSData)

m3.1c <- lm(polintr ~ unempdummy + gndr + eisced + uniondummy, data = ESSData)

m3.1blabels <- c("Unemployment","Gender","Less than secondary","Lower secondary","L. Tier Upper Secondary","U. Tier Upper Secondary","Advanced Vocational","BA","MA")

stargazer::stargazer(m3.1a, m3.1b, m3.1c, covariate.labels = m3.1blabels, type = "html")


```  

## Inferential Statistics III: Political Interest ##  {.morereduced}

<div class="columns-2">

```{r, echo=F, results='asis'}

m3.1c <- lm(polintr ~ unempdummy + gndr + eisced + uniondummy + factor(cntry) - 1, data = ESSData)

stargazer(m3.1c, type = "html", digits = 2)

#stargazer::stargazer(m3.1c, type = "html")


```
</div>


## Inferential Statistics III: Political Interest ## {.smaller}

```{r, echo = F}

m3.1cframe <- data.frame(Variable = rownames(summary(m3.1c)$coef), Coefficient = summary(m3.1c)$coef[,1], SE = summary(m3.1c)$coef[,2], modelName = "Country Model")

m3.1cframe <- m3.1cframe[-c(1,2,3,4),]

m3.1cframe$Variable <- c("BE","BG","CY","CZ","DE","DK","EE","ES","FI","FR","GB","GR","HU","IE","IT","NL","NO","PL","PT","SE","SI","SK")

# Specify the width of your confidence intervals
interval1 <- -qnorm((1-0.9)/2)  # 90% multiplier
interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier

# Plot

zp1 <- ggplot(m3.1cframe)

zp1 <- zp1 + geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                                ymax = Coefficient + SE*interval1),
                            lwd = 1, position = position_dodge(width = 1/2))
zp1 <- zp1 + geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
                                 ymax = Coefficient + SE*interval2),
                             lwd = 1/2, position = position_dodge(width = 1/2),
                             shape = 21, fill = "WHITE")
zp1 <- zp1 + ggtitle("Comparing Various Country Coefficients") + 
  theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5), 
        axis.text.x = element_text(face = "bold"), 
        axis.title.y = element_text(face = "bold")) + 
  labs(x = "Countries") 
print(zp1)  # The trick to these is position_dodge()



# Notes:

# Italy - only 2002, 2004 and 2012

```

<div class="centered">
Remember, a lower number (i.e., closer to 1) equates to a higher political interest. 
</div>


## Concluding Thoughts ## 

- An unemployed young person will have a lower political interest than an employed young person

- At higher levels of education, individuals indicate higher political interest

- A person's country of residence also clearly affects their level of political interest

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; This conditions the effect of unemployment on political 
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; interest

## Where to from here? ## {.build}

- <b>Want to introduce new types of models in the paper</b>

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Will likely need to make use of logit models when analyzing 
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; voting and demonstration habits

- <b>Integration of additional data</b>

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; There is a 7th round of ESS data that we were unable to
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; successfully merge with our current dataset

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Would like to continue to work on this to increase the range
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; of data available to us

## Thank you! ##

Questions?
