
---
title: "The Effect of Youth Unemployment on Youth Political Engagement"
author: "Tori Dykes & Mansi Wadhwa"
date: "11/28/2016"
output: ioslides_presentation
---

```{r, warnings=F, message=F, echo=F, include=FALSE}

source("PresentationDataCleaning.R")

```

## Research Question

- How does youth unemployment affect youth political engagement within European countries?
  
- Does it inspire **apathy** or **action**?


## Data Sources

We used two main datasets for our research:

**The European Social Survey**

- Representative survey of EU residents conducted every two years (we used data from 2002 - 2012)

- Respondents are asked about their opinions and attitudes on a variety of political and social topics

- Subsetted data to only look at youths 18 - 25

**Eurostat Data**

- Used their data on yearly youth unemployment rates in various European countries 


## Descriptive Statistics

- Show some ranges of values across countries
- Nice ggplot graphs here

## Inferential Statistics I

- Attempt at regressing change in a given political engagement variable on change in unemployment
- Explain lack of significance

## Inferential Statistics II

- Attempt at regressing given political engagement variable on response to whether or not youth unemployed in last XX months
- Variables to look at:
  - Polintr
  - Pbldmn
  - Vote

Control Variabls:
  - eisced
  - pdjobev
  - Countries
  - mbtru
  - gndr
  - stfdem

## Inferential Statistics III: Political Interest ##  {.smaller}
```{r, echo=F, results = 'asis'}
## Models for Unemployment ##

# maybe helpful for font sizes: http://www.itgo.me/a/4995744297035700956/resize-stargarzer-table-when-type-html-for-ioslides-in-rstudio

# Political Interest 

m2.1a <- lm(polintr ~ unempdummy, data = ESSData)

m2.1blabels <- c("Unemployment","Gender","Less than secondary","Lower secondary","L. Tier Upper Secondary","U. Tier Upper Secondary","Advanced Vocational","BA","MA")

m2.1b <- lm(polintr ~ unempdummy + gndr + factor(eisced) - 1, data = ESSData)

stargazer::stargazer(m2.1a, m2.1b, covariate.labels = m2.1blabels, type = "html")


```  

## Inferential Statistics III: Participation in Public Demonstrations ## 

```{r, echo=F, results = 'asis'}

# Public Demonstration

m2.2 <- lm(pbldmn ~ unempdummy, data = ESSData)

stargazer::stargazer(m2.2, type = "html")


```

## Avenues for further research

- How could this question be better answered?
- What data would be needed?

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

<div class="centered">
This text is centered.
</div>


<div class="red2">
This text is red
</div>

## Slide with Interactive Plot


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```


