
---
title: "The Effect of Youth Unemployment on Youth Political Engagement"
author: "Tori Dykes & Mansi Wadhwa"
date: "12/2/2016"
output: ioslides_presentation
css: styles.css

---

```{r, warnings=F, message=F, echo=F, include=FALSE}

source("PresentationDataCleaning.R")

```

## Research Question

- How does youth unemployment affect youth political engagement within European countries?
  
- Does it inspire **apathy** or **action**?


## Data Sources

We used two main datasets for our research:

**The European Social Survey**

- Representative survey of EU residents conducted every two years (we used data from 2002 - 2012)

- Respondents are asked about their opinions and attitudes on a variety of political and social topics

- Subsetted data to only look at youths 18 - 25

**Eurostat Data**

- Used their data on yearly youth unemployment rates in various European countries 


## Descriptive Statistics

- Show some ranges of values across countries
- Nice ggplot graphs here

## Inferential Statistics I {.smaller .build}

- Original intent was to regress the change in a given political variable on the change in unemployment

- Became clear we simply didn't have the right data / enough data to do this meaningfully

<div class="columns-2">

```{r, echo = F, results='asis'}

m1.1 <- lm(deltaavgpolintr ~ deltavalue, data = YouthData)

m1.1labels <- c("Delta Unemployment")
stargazer::stargazer(m1.1, covariate.labels = m1.1labels, type = "html")

m1.2 <- lm(deltaavgvote ~ deltavalue, data = YouthData)

stargazer::stargazer(m1.2, covariate.labels = m1.1labels, type = "html")


```

</div>

## Inferential Statistics II

- Since we have access to a host of individual-level data in the ESS survey, including unemployment, decided to look here instead

- Consider three political participation variables:

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Level of political interest

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Participation in public demonstrations

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Voting

```{r, echo=F}
# should voting be a logit instead?? same with pbldmn


#Control Variables:
# - eisced
# - pdjobev
# - Countries
# - mbtru
# - gndr
# - stfdem

```

## Inferential Statistics III: Political Interest ##  {.morereduced}
```{r, echo=F, results = 'asis'}
## Models for Unemployment ##

# maybe helpful for font sizes: http://www.itgo.me/a/4995744297035700956/resize-stargarzer-table-when-type-html-for-ioslides-in-rstudio

# Political Interest 

m3.1a <- lm(polintr ~ unempdummy, data = ESSData)

m3.1b <- lm(polintr ~ unempdummy + gndr + factor(eisced) - 1, data = ESSData)

m3.1c <- lm(polintr ~ unempdummy + gndr + factor(mbtru) - 1, data = ESSData)

m3.1blabels <- c("Unemployment","Gender","Less than secondary","Lower secondary","L. Tier Upper Secondary","U. Tier Upper Secondary","Advanced Vocational","BA","MA","Curr. Memb. of Trade Union","Prev. Memb. of Trade Union","Not Memb. of Trade Union")

stargazer::stargazer(m3.1a, m3.1b, m3.1c, covariate.labels = m3.1blabels, type = "html")


```  

## Inferential Statistics III: Political Interest ##

```{r, echo = F}

library(sjPlot)

sjp.setTheme(title.align = "center", title.size = 1.5)
sjp.grpfrq(ESSData$eisced, ESSData$polintr, show.prc = F, show.n = F, 
           axis.titles = c("Education Levels","Frequency"), 
           axis.labels = c("Less than Secondary","Lower \nSecondary","Lower Tier Upper \nSecondary",
                           "Upper Tier Upper \nSecondary","Advanced Vocational","BA","MA"),
           title = c("Distribution of Political Interest by Educational Level"))

```

## Inferential Statistics III: Political Interest ##  {.reduced}

<div class="columns-2">

```{r, echo=F, results='asis'}

m3.1c <- lm(lm(polintr ~ unempdummy + gndr + factor(cntry) - 1, data = ESSData))

stargazer(m3.1c, type = "html", digits = 2)

#stargazer::stargazer(m3.1c, type = "html")


```
</div>


## Inferential Statistics III: Participation in Public Demonstrations ## 


```{r, echo=F, results = 'asis'}

# Public Demonstration

m2.2 <- lm(pbldmn ~ unempdummy, data = ESSData)

stargazer::stargazer(m2.2, type = "html", font.size = "tiny")


```


## Avenues for further research

- How could this question be better answered?
- What data would be needed?

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

<div class="centered">
This text is centered.
</div>


<div class="red2">
This text is red
</div>

## Slide with Interactive Plot


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```


