
---
title: "The Effect of Youth Unemployment on Youth Political Engagement"
author: "Tori Dykes & Mansi Wadhwa"
date: "11/28/2016"
output: ioslides_presentation
runtime: shiny
---

```{r, warnings=F, message=F, echo=F, include=FALSE}

source("PresentationDataCleaning.R")

```

## Research Question

- How does youth unemployment affect youth political engagement within European countries?
  
- Does it inspire **apathy** or **action**?


## Data Sources

We used two main datasets for our research:

**The European Social Survey**

- Representative survey of EU residents conducted every two years (last round of data available is from 2014)

- Respondents are asked about their opinions and attitudes on a variety of political and social topics

- Subsetted data to only look at youths 18 - 25

**Eurostat Data**

- Used their data on yearly youth unemployment rates in various countries 

## Descriptive Statistics

- Show some ranges of values across countries
- Nice ggplot graphs here

## Inferential Statistics I

- Attempt at regressing change in a given political engagement variable on change in unemployment
- Explain lack of significance

## Inferential Statistics II

- Attempt at regressing given political engagement variable on response to whether or not youth unemployed in last XX months
- Variables to look at:
  - Polintr
  - Pbldmn
  - Vote

Control Variabls:
  - edulvla
  - pdjobev
  - Countries
  - mbtru
  - gndr
  - stfdem

## Inferential Statistics III: Political Interest ## 
```{r, echo=F, results = 'asis'}
## Models for Unemployment ##

# maybe helpful for font sizes: http://www.itgo.me/a/4995744297035700956/resize-stargarzer-table-when-type-html-for-ioslides-in-rstudio

# Political Interest 

#m2.1 <- lm(polintr ~ unempdummy, data = ESSData)

#summary(m2.1)

#stargazer::stargazer(m2.1, type = "html")


```  

## Inferential Statistics III: Participation in Public Demonstrations ## 

```{r, echo=F, results = 'asis'}

# Public Demonstration

#m2.2 <- lm(pbldmn ~ unempdummy, data = ESSData)

#stargazer::stargazer(m2.2, type = "html")


```

## Avenues for further research

- How could this question be better answered?
- What data would be needed?

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

<div class="centered">
This text is centered.
</div>


<div class="red2">
This text is red
</div>

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```


