
---
title: "The Effect of Youth Unemployment on Youth Political Engagement"
author: "Tori Dykes & Mansi Wadhwa"
date: "11/28/2016"
output: ioslides_presentation
runtime: shiny
---

## Research Question

## Data Sources

- ESS Data
- Eurostat Data

## Descriptive Statistics

- Show some ranges of values across countries
- Nice ggplot graphs here

## Inferential Statistics I

- Attempt at regressing change in a given political engagement variable on change in unemployment
- Explain lack of significance

## Inferential Statistics II

- Attempt at regressing given political engagement variable on response to whether or not youth unemployed in last XX months

## Avenues for further research

- How could this question be better answered?
- What data would be needed?

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

<div class="centered">
This text is centered.
</div>


<div class="red2">
This text is red
</div>

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```


